Results

### 2024-09-16 scripts/Results.Rmd
psummarizing number and sizes of patches

  wide <- dplyr::mutate(
    x, 
    suitability = suitability, 
    .before = geometry) |>
    dplyr::select(-f_rankedp, -f_patchMetrics, -f_classMetrics) |>
    dplyr::left_join(lsm, by = c('PchIDComb' = 'id' ))

@@

Some of these visits undoubtedly arose due to revisits of known occurrences. 
We will discard any point within 500m of an historic point which we know was distributed to the crews via QGIS. 
```{r}
p <- '../data/raw/occurrence/combined_records'
f <- file.path(p, list.files(p, pattern = '.shp$'))

f_occ <- data.frame(
  f_rankedp = f, 
  taxa = gsub('[.]shp$', '', basename(f))
)

@@

  occurrences <- sf::st_read(sf::st_drop_geometry(x$f_rankedp[1]), quiet = T) |>
    sf::st_buffer(1000)

@@

  return(dplyr::select(x, -f_rankedp))
}

@@

suitability_amounts <- readRDS('../data/processed/prcntSDMsurfaceSuitable.rds') |>
  bind_rows(suitability_amounts)

@@

## Determine which points were used in training the models

These points will need to be removed because they are already known to be presences...

>>>>

  wide <- dplyr::mutate(
    x, 
    suitability = suitability, 
    .before = geometry) |>
    dplyr::select(-f_patchMetrics, -f_classMetrics) |>
    dplyr::left_join(lsm, by = c('PchIDComb' = 'id' ))

@@

Some of these visits undoubtedly arose due to revisits of known occurrences. 
We will discard any point within 1000m of an historic point which we know was distributed to the crews via QGIS. 
```{r}
p <- '../data/raw/occurrence/combined_records'
f <- file.path(p, list.files(p, pattern = '.shp$'))

f_occ <- data.frame(
  f_occ = f, 
  taxa = gsub('[.]shp$', '', basename(f))
)

@@

  occurrences <- sf::st_read(sf::st_drop_geometry(x$f_occ[1]), quiet = T) |>
    sf::st_buffer(1000)

@@

  return(dplyr::select(x, -f_occ))
}

@@

suitability_amounts <- readRDS('../data/processed/prcntSDMsurfaceSuitable.rds') |>
  bind_rows()

@@

Connectivity analysis

```{r}
ggplot () + 
  geom_bar(data = files, aes(Rank))

# What distribution of these ranks exist within the data sets? - Let's show 
# the proportion which is returned by all.

PatchSummary <- function(x){

  patches <- sf::st_read(x, quiet = TRUE)

  area_rank <- patches |>
    dplyr::group_by(Rank) |>
    dplyr::summarise(geometry = sf::st_union(geometry))

  area_rank <- data.frame(
    Taxon = gsub('[.]shp$', '', basename(x)),
    dplyr::select(sf::st_drop_geometry(area_rank), 'Rank'),
    Area_ha = as.numeric(units::set_units(sf::st_area(area_rank), 'ha'))
  )

  cts_rank <- patches |>
    sf::st_drop_geometry() |> 
    dplyr::select(Rank) |>
    dplyr::count(Rank, name = 'Patches') |>
    dplyr::left_join(area_rank, by = 'Rank') |>

    # now calculate as proportions
    dplyr::ungroup() |>
    dplyr::mutate(
      Patches = Patches/sum(Patches),
      Area_ha = Area_ha/sum(Area_ha)
    ) |>
    dplyr::relocate(Taxon, .before = Rank)

  return(cts_rank)

need_patches <- unique(files$f_rankedp)
patch_summs <- lapply(need_patches, PatchSummary)
